A thesis draft

### 2018-10-31 res/sections/10-ProjectAnalysis.tex
Add partial SFC introduction

>>>>

Even though SFCs and VNFs are part of the ETSI architecture, the complexity 
behind was so high to require particular care and a separated study. Indeed, 
the  SFCs are the core of the whole project: packet transmission and 
elaboration is made here. Challenges regarding this topic are building a 
system that is flexible enough to allow dynamic packet routing, support 
scalability and provide methods to recovery from failures. With this challenges 
packet transmission revealed to be a foundamental point to choose carefully.
